Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-04 lqg-strings.tex
added a paragraph in discussion section about what vector excitations of closed string could relate to

>>>>

In section \ref{sec:quantum-KG-string} we saw that our model allows closed string spin-1 excitations at the first level, which is due to our solution not having independent left and right sectors. Closed string excitations are usually related to the gravitational field and background spacetime itself, so what could the first level vector states of the closed string relate to? Well, in section \ref{sec:gauging-lt} we discussed about a possible formulation of ST in terms of a Lorentz connection $\mc{A}_{\mu}$, which is an ingredient in describing the gravitational field in Einstein-Cartan [ref] formulation, and so this seems to be the natural candidate as to what the first level vector excitation of the closed string could be,
\begin{equation} \label{eqn:connection-string-vector-excitation}
	\mc{A}_{\mu} \sim \eta _{\mu \nu} (\Hat{a}^{\nu} _{1})^{\dagger} \ket{0} .
\end{equation}
Another candidate for what the vector excitations could relate to is the Ashtekar electric fields $\widetilde{E}^{\mu} _{I}$,
\begin{equation} \label{eqn:AEF-string-vector-excitation}
	\widetilde{E}^{\mu} _{I} \sim (\Hat{a}^{\mu} _{I})^{\dagger} \ket{0} .
\end{equation}
